\ProvidesFile{template.tex}
    [2013/04/16 v3.2013^^J%
     Template file for NDdiss2e class by Sameer Vijay and updated by Megan Patnott^^J]
\documentclass[noinfo,final,sort&compress]{nddiss2e}
% One of the options draft, review, final must be chosen.
% One of the options textrefs or numrefs should be chosen
% to specify if you want numerical or ``author-date''
% style citations.
% Other available options are:
% 10pt/11pt/12pt (available with draft only)
% twoadvisors
% noinfo (should be used when you compile the final time
%         for formal submission)
% sort (sorts multiple citations in the order that they're
%       listed in the bibliography)
% compress (compresses numerical citations, e.g. [1,2,3]
%           becomes [1-3]; has no effect when used with
%           the textrefs option)
% sort&compress (sorts and compresses numerical citations;
%           is identical to sort when used with textrefs)

\usepackage{bm} 
\usepackage{tikz}
\usetikzlibrary{shapes,arrows}
\usepackage{pdflscape}
\usepackage[version=3]{mhchem}
\usepackage{mathtools}
\usepackage{abraces}
\usepackage{threeparttable}
\usepackage{multirow}
\usepackage{dcolumn}
\usepackage[export]{adjustbox}
\usepackage{mathrsfs}
\usepackage{ragged2e}
\usepackage{csquotes}
\usepackage{adjustbox}

\newcommand{\degree}{\ensuremath{^\circ}}

\begin{document}

\frontmatter % All the items before the first chapter go in ``frontmatter''

\title{EXPLORATION OF INTERFACIAL THERMAL CONDUCTANCE OF GOLD NANOPARTICLES USING MOLECULAR DYNAMICS}
\author{Suzanne M. Neidhart}
\work{Dissertation}
\degaward{Doctor of Philosophy}
\advisor{J. Daniel Gezelter}
\department{Chemistry and Biochemstry}
\maketitle

%\copyrightholder{Suzanne M. Neidhart} 
%\copyrightyear{2018}           
%\makecopyright

\begin{abstract}
In this dissertation I present work on the factors important to heat transport in gold nanostructures, particularly nanoparticles. I examine the effect of particle size, ligand layer rigidity, and surface gold vibrational freedom. The interfacial thermal conductance of various particle morphologies, as well as the thermal conductivity of nanoarrays, display trends of how heat transport is affected by particle size, shape, and volume fraction of a system.
Direct simulations of interfacial thermal conductance of solvated gold nanoparticles were carried out using molecular dynamics. 
%All particle simulations used the Langevin Hull method for non-periodic systems.

Nanoparticles created in vitro contain a ligand layer at the surface of each particle that prevents aggregation and is a result of the method used in the synthesis of the particles. This moiety controls the movement of heat from a particle to the surrounding media. In particular, Chapter \ref{chapter:NPthiols} looks closely at how the rigidity of this ligand layer (and the length of the ligand) change thermal transport across the solvent-particle interface. This provides further insight into the factors that govern heat flow. Proposed mechanisms for heat transfer rely on two effects: the vibrational spectral overlap of the materials at the interface and the physical contact between the same materials.

Finding no direct relationship between particle size with the ligand layer and the thermal transport, a simpler system was examined: bare nanoparticles in a non-polar solvent.
The particles consist of nanospheres, icosahedra, and cuboctahedra. The latter two structures display facets that are common in many nanostructures due to their stability.
The interfacial thermal conductance (G) of the particles was examined as a function of particle radius and morphology. The coordination of gold atoms at the particle surface, which provides information about the vibrational spectrum, displayed a small correlation with G. This lends support to the proposed factors for heat transport that were discovered while investigating ligands.

The ideas from both previous chapters are combined to study \ce{Au144PET60} particles, in both isolation, and in a nanoarray. These small particles ($r \approx 10$ \AA) have highly undercoordinated gold atoms in the ligand layer. The thermal conductivity of the composite material is predicted using bulk properties and an estimation of boundary resistance. This prediction uses individual components of the composite systems, and is compared to results for simulated nanoarrays. In the predicted conductivity, the nanoarray thermal conductivity depends mostly on the geometric feature, $v_p$, the particle volume fraction. 

\end{abstract}

% \renewcommand{\dedicationname}{NEW DEDICATION NAME}
% \begin{dedication}
% \end{dedication}

\tableofcontents
\listoffigures
\listoftables

%\begin{preface}
%\vfill
%\begin{flushright}
%\textit{''Some say the world will end in fire,} \\
%textit{Some say in ice.''}\\
%--Robert Frost
%\end{flushright}
%\vfill
%\end{preface}

\begin{acknowledge}
First, I would like to thank my advisor, Professor J. Daniel Gezelter, for his persitent guidance and support throughout this research. My time in graduate school has been greatly enriched by having such a wonderful mentor.
His patience for all the little questions and concern for the individual's growth has been unmatched.

I am grateful to my committee, Professor J. Daniel Gezelter, Professor Steven A. Corcelli, and Professor William F. Schneider for their insightful questions and helpful suggestions in navigating this research.
Additionally, I would like to thank Professor Christine M. Aikens for her continual mentorship and guidance during transition periods of my career.
I am grateful to past group members, especially Dr. Shenyu Kuang, Dr. Kelsey M. Stocker, Dr. Joseph R. Michalka, Dr. Madan Lamichhane, Dr. Patrick B. Louden, and Thomas Parsons for laying the foundations of the research, helpful conversations, and continuously challenging me to be a better scientist.
I am very thankful for the current group members, Hemanta Bhattarai, Alexander Mazanek, Cody Drisko, and Nicholas Milikich for the helpful discussions, research related and otherwise.
I would also like to acknowledge the Corcelli group, in particular Dr. Mary Sherman and Dr. Clyde A. Daly Jr., for their useful discussions and camaraderie. 

Throughout my time spent at Notre Dame, I have been blessed with great friendships that have made the path through graduate school brighter, that I would be remiss to not mention: Ruthie Nelson, Claire Bowen, Ju-Young Kim, Arielle Lopez, Rachel Miller, Madeline Smith, Jeremy Eberle, and Melissa Hofferbaur. 
In particular I would like to thank the Association for Women in Science, a group that created an instant community and through which I formed strong friendships.

In addition to all the above, I would like to acknowledge my family for their support throughout my life. 
Many thanks to my siblings, for all the phone calls, visits, and encouragement over the years.
And to my parents, for whom I would not be where I am today without their years of sacrifice and continued love and support.

Finally, I would like to thank my husband and best friend, Peter Neidhart. His support and understanding throughout our time at Notre Dame has been essential for the completion of this document, and he continues to bring happiness to my life. 
%
\end{acknowledge}

\mainmatter

%\bibpunct{[}{]}{,}{n}{,}{,}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%		CHAPTER 1 -- INTRODUCTION
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\include{chapters/Introduction}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%		CHAPTER 2 -- Ligand Dependence of the Thermal Conductivity
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\include{chapters/NPthiols}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%		CHAPTER 3 -- Morphology Dependence of the Interfacial Thermal Conductance
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\include{chapters/Morph}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%		CHAPTER 4 -- Staple Motifs
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\include{chapters/Arrays}


%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%		CHAPTER 5 -- Conclusion
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\include{chapters/Conclusion}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%		UNNUMBERED CHAPTER
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% \unnumchapter{FEATURES OF FORMATTING IN THIS EXAMPLE FILE}
% The \unnumchapter command allows you to include an unnumbered chapter as part of
% the main text before Chapter 1. It will appear in your table of contents, and you
% should have at most one such chapter (although nothing in the class file will
% prevent you from creating more).

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%		APPENDIX
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%\appendix
%\include{Chapters/appendix1}
%\include{Chapters/structuralAppendix}
%\include{Chapters/dynamicAppendix}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%		BACK STUFF
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

% % comment out the following three lines
% if using chapter-wise bibliography

 \backmatter
 
%\bibliographystyle{nddiss2e}
%\bibliographystyle{nddiss2enoarticletitles}
\bibliographystyle{achemso}
%\bibliographystyle{abbrvnat} 
\bibliography{Neidhart_Thesis} 
 
 
\end{document}

\endinput
