\chapter{CONCLUSION}\label{chap:conclusion}
In this dissertation applications of Reverse Non-Equilibrium Molecular Dynamics and the Langenvin Hull method were applied to gold nanoparticle systems. Gold nanoparticle systems have well characterized optical properties, but less explored thermal properties, which are typically important after the electronic excitation. The simulations in previous chapters explored the effect of ligand rigidity, gold particle morphology, and staple motif effects in nanoarrays through molecular dynamics.

Understanding how the capping agent, or ligand, on gold nanoparticles interacts with the particle and solvent environment is essential to predicting behavior of nanoparticles in a given system. The effect of adding rigidity to the ligand layer, changed the penetration accessibility of the interfacial solvent. With a more rigid ligand, generally the solvent has an increased penetration in the ligand layer. This lead to a stronger vibrational overlap of the ligand and solvent, and thus a better thermal transport. Additionally, the addition of the ligand layer aids interfacial thermal conductivity. The sulfur on the thiolate ligand acts as a strong conduit for heat from the particle to the solvent.

Though the ligand layer is experimentally interesting and has promising characteristics for tailoring a nanoparticle for desired thermal and optical properties, a bare particle gives insight to how the morphology of the gold particle affects thermal transport.
From simulations of spheres, cuboctahedra, and icosahedra; the surface of the gold particle is essential to thermal transport from bare particles.
Furthermore, work in chapter 3 displayed that the underlying lattice carries important information on the available low frequency phonon modes. 

In an effort examine both the ligand and undercoordination of gold atoms at the surface within the same system, chapter 4 investigates the effect of the staple motif on \ce{Au144PET60} nanoclusters.
The nanoparticles were examined in two different solvents; one polar and one non-polar; in single particle systems and in arrays.
While the array systems have inconclusive results, the single particle systems display interesting behavior in respect to the ligand/solvent interaction. 
The major contributing factor to the interfacial thermal conductivity was the solvent's ability to penetrate into the ligand layer. While the staple motif might have increased the conductivity through the undercoordinated gold atoms in the ligand, the solvent ultimately was the limiting piece of the system. 
Additionally, the solvent thermal conductivity due to the partial volume becomes the dominating factor in the predictive equation for thermal conductivity through an array of \ce{Au144PET60} particles.

In the future, work on more biologically relevant systems would be an interesting avenue to explore. 
With a new polarizable metal model (DR-EAM), the gold substrate would be able to more appropriately interact with polar molecules.
Thus, a good starting system would be a gold slab displaying (111) facets in water.

To systematically determine how polarization affects thermal conductivity in a simple gold/water system, each of the components should be tested individually. Therefore the following systems would be examined: Au(EAM)/\ce{H20}(TIP-4P),  Au(EAM)/\ce{H2O}(TIP-4P-fq),  Au(DR-EAM)/\ce{H2O}(TIP-4P),  and Au(DR-EAM)/\ce{H2O}(TIP-4P-fq).
If the polarization of the gold and water effects the the interfacial thermal conductivity of the system, moving forward with biologically relevant systems would be the next course of action.
Various interesting ligands such as: thiolated PEG, citrate, Cetyl trimethylammonium bromide(CTAB), and different carboxylic acid moieties; could be tested on planar and spherical systems. The differences in these could then be identified to tailor nanoparticles for different thermal needs.

In addition to the further work needed in the gold nanoparticle systems, the trend in pure solvents would be an interesting avenue to explore.
In chapter 4, the two solvents (dichloromethane and toluene) had very different thermal conductivity values at the three box lengths simulated but had the same infinite box length bulk thermal conductivity.
Dicholormethane, with a density of $\approx$ 2x that of toluene, had a clear box length dependence, while toluene did not. 
It would be interesting to follow these simulations with a range of different common solvents, with known thermal conductivities, and look not only at the box dependences but a normal mode analysis.
In the more dense fluids it is possible that the imaginary frequencies would be more heavily populated, leading to higher bulk thermal conductivities.

The work presented in this work has shown significant progress in identifying the trends that are important for controlling the thermal properties of gold nanoparticles. Moving forward, work with polarizable force fields, biologically relevant ligands and capping agents, and elucidating trends in solvent thermal conductivity would move nanoparticle design forward.
